Parallel Information Set Generation for Kriegspiel

### 2012-07-15 sbac/paper.tex
Removed superfluous figure reference
Edited abstract

\author{Mark Richards, Abhishek Gupta, Osman Sarood and Laxmikant V. Kale\\
Department of Computer Science\\ 
University of Illinois\\ 
Urbana, IL\\ {mdrichar, gupta59, sarood1, kale}@illinois.edu\\
% For a paper whose authors are all at the same institution, 
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'', 
% just like the second author.
%\and
%Second Author\\
%Institution2\\
%First line of institution2 address\\ Second line of institution2 address\\ 
%SecondAuthor@institution2.com\\
}

@@

\begin{abstract}
Information Set Generation is the identification of the set of paths in an
imperfect information game tree that are consistent with a player's
observations.  The ability to reason about the possible game history is
critical to the performance of game-playing agents.  ISG represent a class of
combinatorial search problems which is computationally intensive but difficult
to efficiently parallelize.

In this paper, we address the parallelization of information set generation in
the context of Kriegspiel (partially observable chess).  We implement the
algorithm on top of a general purpose combinatorial search engine and discuss
its performance under different load balancing strategies and with different
grainsize parameters.  We achieve speedups of over 500 on 1,024 processors, far
exceeding previous scalability results for game tree search applications.
\end{abstract}

>>>>

\author{
\IEEEauthorblockN{Mark Richards, Abhishek Gupta, Osman Sarood and Laxmikant V. Kal\'e\\}
\IEEEauthorblockA{University of Illinois at Urbana-Champaign\\
Urbana, IL 61801, USA\\
(mdrichar, gupta59, sarood1, kale)@illinois.edu\\}
% For a paper whose authors are all at the same institution, 
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'', 
% just like the second author.
%\and
%Second Author\\
%Institution2\\
%First line of institution2 address\\ Second line of institution2 address\\ 
%SecondAuthor@institution2.com\\
}

@@

\begin{abstract}
Information Set Generation (ISG) is the identification of the set of paths in an
imperfect information game tree that are consistent with a player's
observations.  The ability to reason about the possible game history is
critical to the performance of game-playing agents.  ISG represents a class of
combinatorial search problems which is computationally intensive but difficult
to efficiently parallelize.

In this paper, we address the parallelization of information set generation in
the context of Kriegspiel (partially observable chess).  We implement the
algorithm on top of a general purpose combinatorial search engine and discuss
its performance using datasets from real game instances in addition to benchmarks. Further, we demonstrate the effect of load balancing strategies, problem sizes and computational granularity (grainsize parameters) on performance.  We achieve speedups of over 500 on 1,024 processors, far
exceeding previous scalability results for game tree search applications.
\end{abstract}
